---
title: "LLM Annotation Sensitivity -- Main Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

```{r setup-libs}
library(tidyverse)

setwd("/home/ck/Documents/Uni/Forschung/Article/2026 - LLM Sensitivity/llm-annotation-sensitivity")

source("run_analysis_new.R")
source("run_table_wide.R")
source("run_pooled_analysis.R")
```

## Load Tweet Data

```{r load-data}

folder_path <- "Tweets_CK"

train_df <- read_csv(file.path(folder_path, "full_train_s.csv"))
test_df  <- read_csv(file.path(folder_path, "full_test_s.csv"))

test_df <- test_df %>% select(all_of(names(train_df)))

tweets_full <- bind_rows(
  train_df %>% mutate(original_split = "train"),
  test_df  %>% mutate(original_split = "test")
) %>%
  rename(
    tweet_id = `tweet.id`,
    hate_speech = `hate.speech`,
    offensive_language = `offensive.language`
  )

summary <- tweets_full %>%
  summarise(
    OL = mean(offensive_language, na.rm = TRUE),
    HS = mean(hate_speech, na.rm = TRUE)
  )

final_summary <- tibble(
  version = "overall",
  OL = summary$OL,
  HS = summary$HS
)

save(tweets_full, final_summary, file = "tweets_data.RData")
```

## Load Models

```{r load-models}

load_model <- function(path, model_name) {
  files <- list.files(path, full.names = TRUE)

  map_df(files, read_csv) %>%
    arrange(batch_id, tweet_in_batch) %>%
    mutate(
      shot = "few-shot",
      model = model_name
    )
}

gpt4    <- load_model("Data_Collection/Models/GPT4o_mini",     "gpt4o_mini")
gpt54   <- load_model("Data_Collection/Models/GPT5.4",         "gpt5.4")
llama4  <- load_model("Data_Collection/Models/Llama4",         "llama4")
mistral <- load_model("Data_Collection/Models/MistralLarge3",  "mistral")

llama31_70b      <- load_model("Data_Collection/Models/Llama3.1_70B_new",    "llama31_70b")
llama31_8b       <- load_model("Data_Collection/Models/Llama3.1_8B_new",    "llama31_8b")
mistral_medium35 <- load_model("Data_Collection/Models/MistralMedium3.5_new", "mistral_medium35")

model_keys <- c(
  "gpt4o_mini", "gpt5.4", "mistral", "mistral_medium35",
  "llama31_8b", "llama31_70b", "llama4"
)

model_labels <- c(
  gpt4o_mini       = "GPT-4o mini",
  gpt5.4           = "GPT-5.4",
  mistral          = "Mistral Large 3",
  mistral_medium35 = "Mistral Medium 3.5",
  llama31_8b       = "Llama 3.1 8B",
  llama31_70b      = "Llama 3.1 70B",
  llama4           = "Llama 4"
)

model_dfs <- list(
  gpt4o_mini       = gpt4,
  gpt5.4           = gpt54,
  mistral          = mistral,
  mistral_medium35 = mistral_medium35,
  llama31_8b       = llama31_8b,
  llama31_70b      = llama31_70b,
  llama4           = llama4
)

save(model_dfs, model_keys, model_labels, file = "model_data.RData")
```

## Run Prevalence Analyses

```{r prevalence-analyses}

load("tweets_data.RData")
load("model_data.RData")

prevalence_results <- imap(model_dfs, function(df, key) {
  run_full_analysis(
    combined_df   = df,
    model_name    = key,
    tweets_full   = tweets_full,
    final_summary = final_summary
  )
})

df_prevalence_all_models <- map_dfr(prevalence_results, "prevalence_data") %>%
  mutate(
    model = factor(
      model_name,
      levels = model_keys,
      labels = model_labels[model_keys]
    )
  )

saveRDS(df_prevalence_all_models, "df_prevalence_all_models.rds")
saveRDS(ref_lines, "ref_lines.rds")
```

```{r prevalence-plot, fig.width=3.5, fig.height=9.5}

df_prevalence_all_models <- readRDS("df_prevalence_all_models.rds")
ref_lines <- readRDS("ref_lines.rds")

combined_prevalence_plot <- ggplot(
  df_prevalence_all_models,
  aes(x = condition_label, y = Value_Pct, color = group_type)
) +

  geom_hline(
    data = ref_lines,
    aes(
      yintercept = intercept,
      linetype = "Reference"
    ),
    color = "gray50",
    linewidth = 0.35,
    show.legend = TRUE
  ) +

  geom_point(
    position = position_dodge(width = 0.55),
    size = 1.6
  ) +

  facet_grid(
    model ~ Measure,
    scales = "fixed",
    labeller = labeller(
      Measure = c(OL = "OL", HS = "HS")
    )
  ) +

  scale_color_manual(
    name = "Condition",
    values = c(
      "base"       = "#443983",
      "conf"       = "#31688e",
      "batch"      = "#35b779",
      "batch_conf" = "#90d743"
    ),
    labels = c(
      "base"       = "Base",
      "conf"       = "+ Conf.",
      "batch"      = "Batch",
      "batch_conf" = "Batch + Conf."
    )
  ) +

  scale_linetype_manual(
    name = NULL,
    values = c("Reference" = "dashed")
  ) +

  scale_y_continuous(
    limits = c(0, 100),
    breaks = c(0, 50, 100),
    expand = expansion(mult = c(0.03, 0.05)),
    labels = function(x) paste0(x, "%")
  ) +

  labs(
    x = "Task Structure",
    y = "Prevalence"
  ) +

  guides(
    color = guide_legend(order = 1, nrow = 2),
    linetype = guide_legend(order = 2)
  ) +

  theme_bw(base_size = 8) +
  theme(
    strip.background = element_blank(),
    strip.text = element_text(size = 7.5, face = "bold"),

    legend.position = "bottom",
    legend.box = "vertical",
    legend.text = element_text(size = 6.5),
    legend.title = element_text(size = 7),
    legend.key.size = unit(0.3, "cm"),

    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(linewidth = 0.2, color = "gray85"),
    panel.border = element_rect(color = "gray75", linewidth = 0.3),

    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 6.5, angle = 0, vjust = 1),
    axis.text.y = element_text(size = 6.5),

    panel.spacing = unit(0.3, "lines"),

    plot.margin = margin(t = 2, r = 2, b = 12, l = 2)
  )

combined_prevalence_plot

ggsave(
  "Plots/combined_prevalences_all_models_acl_halfpage.pdf",
  combined_prevalence_plot,
  device = cairo_pdf,
  width = 8.8,
  height = 24,
  units = "cm"
)
```

## Prevalence Heatmap (Deviation from Human Reference)

```{r prevalence-heatmap, fig.width=9, fig.height=5}

df_prevalence_all_models <- readRDS("df_prevalence_all_models.rds")
ref_lines <- readRDS("ref_lines.rds")

group_map <- c(base = "B", conf = "+C", batch = "Bt", batch_conf = "Bt+C")
cond_map  <- c(
  "Joint,\nOL first" = "J-OL",
  "Joint,\nHS first" = "J-HS",
  "Separate"         = "Sep"
)

### Fixed 12-column order: 3 conditions x 4 group types, condition-major
x_level_order <- tidyr::crossing(
  cond  = factor(names(cond_map),  levels = names(cond_map)),
  group = factor(names(group_map), levels = names(group_map))
) %>%
  mutate(x_label = paste(cond_map[as.character(cond)], group_map[as.character(group)], sep = "\n")) %>%
  pull(x_label)

measure_full <- c(OL = "Offensive Language", HS = "Hate Speech")

facet_lookup <- ref_lines %>%
  arrange(Measure) %>%
  mutate(facet_label = paste0(measure_full[as.character(Measure)], "  (ref=", round(intercept), "%)"))

df_heatmap <- df_prevalence_all_models %>%
  left_join(ref_lines, by = "Measure") %>%
  left_join(facet_lookup %>% select(Measure, facet_label), by = "Measure") %>%
  mutate(
    deviation   = Value_Pct - intercept,
    x_label     = factor(
      paste(cond_map[as.character(condition_label)], group_map[as.character(group_type)], sep = "\n"),
      levels = x_level_order
    ),
    facet_label = factor(facet_label, levels = facet_lookup$facet_label)
  )

### Symmetric color limits, rounded up to the nearest 5 pts
dev_limit <- ceiling(max(abs(df_heatmap$deviation), na.rm = TRUE) / 5) * 5

df_heatmap <- df_heatmap %>%
  mutate(text_color = if_else(abs(deviation) > dev_limit * 0.55, "white", "grey15"))

prevalence_heatmap <- ggplot(
  df_heatmap,
  aes(x = x_label, y = fct_rev(model), fill = deviation)
) +

  geom_tile(color = "white", linewidth = 0.6) +

  geom_text(
    aes(label = sprintf("%+.0f", deviation), color = text_color),
    size = 2.5
  ) +

  geom_vline(xintercept = c(4.5, 8.5), color = "white", linewidth = 1.4) +

  facet_wrap(~ facet_label, nrow = 1) +

  scale_fill_distiller(
    palette   = "RdBu",
    direction = -1,
    limits    = c(-dev_limit, dev_limit),
    name      = "Deviation from\nreference (pts)"
  ) +

  scale_color_identity() +

  labs(x = NULL, y = NULL) +

  theme_minimal(base_size = 9) +
  theme(
    panel.grid       = element_blank(),
    strip.background = element_blank(),
    strip.text       = element_text(face = "bold", size = 10),
    axis.text.x      = element_text(size = 6.5, lineheight = 0.85),
    axis.text.y      = element_text(size = 8),
    legend.position  = "right"
  )

prevalence_heatmap

ggsave(
  "Plots/prevalence_heatmap_all_models.pdf",
  prevalence_heatmap,
  device = cairo_pdf,
  width  = 22,
  height = 11,
  units  = "cm"
)
```

### Stacked Version (OL Above HS)

```{r prevalence-heatmap-stacked, fig.width=6.5, fig.height=9.5}

prevalence_heatmap_stacked <- prevalence_heatmap +
  facet_wrap(~ facet_label, ncol = 1, scales = "free_x") +
  theme(
    axis.text.x    = element_text(size = 7, lineheight = 0.85),
    legend.position = "bottom"
  ) +
  guides(fill = guide_colorbar(title.position = "top", barwidth = unit(6, "cm")))

prevalence_heatmap_stacked

ggsave(
  "Plots/prevalence_heatmap_all_models_stacked.pdf",
  prevalence_heatmap_stacked,
  device = cairo_pdf,
  width  = 16,
  height = 24,
  units  = "cm"
)
```

### Flipped Axis (Model on X, Condition on Y)

```{r prevalence-heatmap-flipped, fig.width=8, fig.height=8}

prevalence_heatmap_flipped <- ggplot(
  df_heatmap,
  aes(x = model, y = fct_rev(x_label), fill = deviation)
) +

  geom_tile(color = "white", linewidth = 0.6) +

  geom_text(
    aes(label = sprintf("%+.0f", deviation), color = text_color),
    size = 2.5
  ) +

  geom_hline(yintercept = c(4.5, 8.5), color = "white", linewidth = 1.4) +

  facet_wrap(~ facet_label, nrow = 1) +

  scale_fill_distiller(
    palette   = "RdBu",
    direction = -1,
    limits    = c(-dev_limit, dev_limit),
    name      = "Deviation from\nreference (pts)"
  ) +

  scale_color_identity() +

  labs(x = NULL, y = NULL) +

  theme_minimal(base_size = 9) +
  theme(
    panel.grid       = element_blank(),
    strip.background = element_blank(),
    strip.text       = element_text(face = "bold", size = 10),
    axis.text.x      = element_text(size = 7, angle = 30, hjust = 1),
    axis.text.y      = element_text(size = 6.5, lineheight = 0.85),
    legend.position  = "right"
  )

prevalence_heatmap_flipped

ggsave(
  "Plots/prevalence_heatmap_all_models_flipped.pdf",
  prevalence_heatmap_flipped,
  device = cairo_pdf,
  width  = 20,
  height = 20,
  units  = "cm"
)
```

### Flipped Axis, Stacked

```{r prevalence-heatmap-flipped-stacked, fig.width=6.5, fig.height=14}

### Spelled-out condition labels, just for this (roomier) version
cond_map_long  <- c("J-OL" = "Joint (OL first)", "J-HS" = "Joint (HS first)", "Sep" = "Separate")
group_map_long <- c("B" = "Base", "+C" = "+ Confidence", "Bt" = "Batch", "Bt+C" = "Batch + Confidence")

x_label_long_lookup <- tidyr::crossing(
  cond  = factor(names(cond_map),  levels = names(cond_map)),
  group = factor(names(group_map), levels = names(group_map))
) %>%
  mutate(
    short = paste(cond_map[as.character(cond)],       group_map[as.character(group)],       sep = "\n"),
    long  = paste(cond_map_long[cond_map[as.character(cond)]], group_map_long[group_map[as.character(group)]], sep = "\n")
  )

x_label_long_map <- setNames(x_label_long_lookup$long, x_label_long_lookup$short)

prevalence_heatmap_flipped_stacked <- prevalence_heatmap_flipped +
  facet_wrap(~ facet_label, ncol = 1, scales = "free_x") +
  scale_y_discrete(labels = x_label_long_map) +
  theme(
    axis.text.x    = element_text(size = 7.5, angle = 30, hjust = 1),
    axis.text.y    = element_text(size = 6.5, lineheight = 1.0),
    legend.position = "bottom"
  ) +
  guides(fill = guide_colorbar(
    title.position = "top", barwidth = unit(6, "cm")
  ))

prevalence_heatmap_flipped_stacked

ggsave(
  "Plots/prevalence_heatmap_all_models_flipped_stacked.pdf",
  prevalence_heatmap_flipped_stacked,
  device = cairo_pdf,
  width  = 14,
  height = 24,
  units  = "cm"
)
```

## Prevalence Heatmap (Deviation from Each Model's Own Mean)

```{r prevalence-heatmap-model-mean-stacked, fig.width=6.5, fig.height=14}

measure_only_label <- c(OL = "Offensive Language", HS = "Hate Speech")

df_heatmap_mm <- df_heatmap %>%
  group_by(model, Measure) %>%
  mutate(
    model_mean      = mean(Value_Pct, na.rm = TRUE),
    deviation_model = Value_Pct - model_mean
  ) %>%
  ungroup() %>%
  mutate(facet_label_mm = factor(measure_only_label[as.character(Measure)], levels = measure_only_label))

### Symmetric color limits, rounded up to the nearest 5 pts
dev_limit_mm <- ceiling(max(abs(df_heatmap_mm$deviation_model), na.rm = TRUE) / 5) * 5

df_heatmap_mm <- df_heatmap_mm %>%
  mutate(text_color_mm = if_else(abs(deviation_model) > dev_limit_mm * 0.55, "white", "grey15"))

### Spelled-out, two-line condition labels (reuses cond_map_long / group_map_long
### and x_label_long_lookup built for the flipped-stacked version above)
x_label_long_map <- setNames(x_label_long_lookup$long, x_label_long_lookup$short)

prevalence_heatmap_model_mean_stacked <- ggplot(
  df_heatmap_mm,
  aes(x = model, y = fct_rev(x_label), fill = deviation_model)
) +

  geom_tile(color = "white", linewidth = 0.6) +

  geom_text(
    aes(label = sprintf("%+.0f", deviation_model), color = text_color_mm),
    size = 2.5
  ) +

  geom_hline(yintercept = c(4.5, 8.5), color = "white", linewidth = 1.4) +

  facet_wrap(~ facet_label_mm, ncol = 1, scales = "free_x") +

  scale_y_discrete(labels = x_label_long_map) +

  scale_fill_distiller(
    palette   = "RdBu",
    direction = -1,
    limits    = c(-dev_limit_mm, dev_limit_mm),
    name      = "Deviation from\nmodel's own mean (pts)"
  ) +

  scale_color_identity() +

  labs(x = NULL, y = NULL) +

  guides(fill = guide_colorbar(
    title.position = "top", barwidth = unit(6, "cm")
  )) +

  theme_minimal(base_size = 9) +
  theme(
    panel.grid       = element_blank(),
    strip.background = element_blank(),
    strip.text       = element_text(face = "bold", size = 10),
    axis.text.x      = element_text(size = 7.5, angle = 30, hjust = 1),
    axis.text.y      = element_text(size = 6.5, lineheight = 1.0),
    legend.position  = "bottom"
  )

prevalence_heatmap_model_mean_stacked

ggsave(
  "Plots/prevalence_heatmap_all_models_vs_model_mean_stacked.pdf",
  prevalence_heatmap_model_mean_stacked,
  device = cairo_pdf,
  width  = 14,
  height = 24,
  units  = "cm"
)
```

## Agreement Analyses (Kappa Heatmaps, All Models)

```{r agreement-analyses}
source("R1c_Agreements_AllModels.R")

load("tweets_data.RData")
load("model_data.RData")

agreement_results <- imap(model_dfs, function(df, key) {
  df_long_model <- run_full_analysis(
    combined_df   = df,
    model_name    = key,
    tweets_full   = tweets_full,
    final_summary = final_summary
  )$df_long

  run_agreement_analysis(
    df_long     = df_long_model,
    model_name  = key,
    tweets_full = tweets_full
  )
})

df_agreement_all_models <- map_dfr(agreement_results, "heat_df") %>%
  mutate(
    model = factor(
      model_name,
      levels = model_keys,
      labels = model_labels[model_keys]
    )
  )

saveRDS(df_agreement_all_models, "df_agreement_all_models.rds")
saveRDS(agreement_results, "agreement_results.rds")
```

```{r agreement-plot, fig.width=6.7, fig.height=8.7}

df_agreement_all_models <- readRDS("df_agreement_all_models.rds")

coolwarm <- colorRampPalette(rev(RColorBrewer::brewer.pal(11, "RdBu")))

task_map <- c(A = "Joint, OL first", B = "Joint, HS first", C = "Separate")

### nested condition labels: task name shown once per block, mode below it
nested_cond_label <- function(x) {
  task_p <- str_extract(x, "^[ABC]")
  occ    <- ave(seq_along(x), task_p, FUN = seq_along)
  mode_p <- case_when(
    x == "gap"                 ~ "",
    x == "reference_agreement" ~ "Ref.",
    grepl("batch_conf", x)     ~ "batch+conf",
    grepl("batch", x)          ~ "batch",
    grepl("conf", x)           ~ "conf",
    TRUE                       ~ "base"
  )
  task_disp <- ifelse(occ == 1 & !is.na(task_p), paste0(task_map[task_p], " "), "")
  paste0(task_disp, mode_p)
}

agreement_heatmap_all_models <- ggplot(
  df_agreement_all_models,
  aes(x = col_cond, y = row_cond, fill = value)
) +

  geom_tile(colour = "white", linewidth = 0.25) +

  geom_text(
    aes(label = ifelse(is.na(value), "",
                        sub("^(-?)0\\.", "\\1.", sprintf("%.2f", value)))),
    size = 1.5
  ) +

  ### rows = model, columns = OL / HS
  facet_grid(model ~ outcome) +

  scale_y_discrete(limits = rev, labels = nested_cond_label) +
  scale_x_discrete(labels = nested_cond_label) +

  scale_fill_gradientn(
    colours  = coolwarm(100),
    limits   = c(0, 1),
    na.value = "white",
    name     = "Kappa"
  ) +

  labs(x = NULL, y = NULL) +

  theme_minimal(base_size = 6) +
  theme(
    panel.grid      = element_blank(),
    axis.text.x     = element_text(size = 4, angle = 90, hjust = 1, vjust = 0.5),
    axis.text.y     = element_text(size = 4),
    strip.text.y    = element_text(size = 5.5, face = "bold", angle = -90),
    strip.text.x    = element_text(size = 6.5, face = "bold"),
    panel.spacing   = unit(0.15, "lines"),
    legend.position = "bottom",
    legend.key.height = unit(0.25, "cm"),
    legend.key.width  = unit(0.6, "cm"),
    legend.title    = element_text(size = 6.5),
    legend.text     = element_text(size = 5.5)
  )

agreement_heatmap_all_models

### sized for ACL's double-column (\textwidth) figure, ~1 page tall
ggsave(
  "Plots/agreements_few_all_models.pdf",
  agreement_heatmap_all_models,
  device = cairo_pdf,
  width  = 17,
  height = 22,
  units  = "cm"
)
```

### Table -- Within-Condition Agreement Only (Diagonal)

```{r agreement-diag-table}
source("R1c_Agreements_AllModels.R")
source("run_table_wide.R")

load("model_data.RData")
agreement_results <- readRDS("agreement_results.rds")

table_agreement_diag_split <- build_agreement_diag_table_split(
  agreement_results = agreement_results,
  model_order        = model_keys,
  model_labels       = model_labels
)

write_csv(table_agreement_diag_split$OL, "Plots/table_agreement_within_condition_OL.csv")
write_csv(table_agreement_diag_split$HS, "Plots/table_agreement_within_condition_HS.csv")

agreement_diag_standalone_tex <- agreement_diag_split_to_standalone_tex(
  table_agreement_diag_split, model_labels[model_keys]
)
writeLines(agreement_diag_standalone_tex, "Plots/table_agreement_within_condition_standalone.tex")

table_agreement_diag_split$OL
table_agreement_diag_split$HS
```

## Run Individual LPM Models

```{r lpm-models}
source("run_inference_analysis_v2.R")

load("model_data.RData")

lpm_results <- imap(model_dfs, function(df, key) {
  run_inference_analysis(
    combined_df = df,
    model_name  = key
  )
})

saveRDS(lpm_results, "lpm_results.rds")
```

## Table -- Wide, All 7 Models

```{r table-wide}

lpm_results <- readRDS("lpm_results.rds")
load("model_data.RData")

table1_wide <- build_wide_table(
  lpm_results  = lpm_results,
  model_order  = model_keys,
  model_labels = model_labels
)

write_csv(table1_wide, "Plots/model_lpm_tables/table1_wide_7models.csv")

table1_wide_latex <- wide_table_to_latex(table1_wide, model_labels[model_keys])
writeLines(table1_wide_latex, "Plots/model_lpm_tables/table1_wide_7models_latex.txt")

table1_wide_standalone_tex <- wide_table_to_standalone_tex(table1_wide, model_labels[model_keys])
writeLines(table1_wide_standalone_tex, "Plots/model_lpm_tables/table1_wide_7models_standalone.tex")

table1_wide
```

## Table -- Pooled Models, LPMs

```{r pooled-lpm-fit}

load("model_data.RData")

pooled_results <- run_pooled_analysis(
  model_dfs    = model_dfs,
  model_labels = model_labels
)

saveRDS(pooled_results, "Plots/combined_inference/pooled_results_lpm.rds")
```

```{r table-pooled}

pooled_results <- readRDS("Plots/combined_inference/pooled_results_lpm.rds")
pooled_dir <- "Plots/combined_inference"

write_csv(pooled_results$combined_paper_table, file.path(pooled_dir, "combined_LPM_paper_table.csv"))

pooled_latex <- combined_pooled_table_to_latex(pooled_results$combined_paper_table, pooled_results$model_level_labels)
writeLines(pooled_latex, file.path(pooled_dir, "combined_LPM_latex_rows.txt"))

pooled_standalone_tex <- combined_pooled_table_to_standalone_tex(
  pooled_results$combined_paper_table,
  model_level_labels = pooled_results$model_level_labels,
  reference_label = pooled_results$reference_label
)
writeLines(pooled_standalone_tex, file.path(pooled_dir, "combined_LPM_standalone.tex"))

write_csv(pooled_results$combined_paper_table_randomslopes, file.path(pooled_dir, "combined_LPM_randomslopes_paper_table.csv"))

pooled_randomslopes_latex <- combined_pooled_table_randomslopes_to_latex(pooled_results$combined_paper_table_randomslopes, pooled_results$model_level_labels)
writeLines(pooled_randomslopes_latex, file.path(pooled_dir, "combined_LPM_randomslopes_latex_rows.txt"))

pooled_randomslopes_standalone_tex <- combined_pooled_table_randomslopes_to_standalone_tex(
  pooled_results$combined_paper_table_randomslopes,
  model_level_labels = pooled_results$model_level_labels,
  reference_label = pooled_results$reference_label
)
writeLines(pooled_randomslopes_standalone_tex, file.path(pooled_dir, "combined_LPM_randomslopes_standalone.tex"))

pooled_results$combined_paper_table
pooled_results$combined_paper_table_randomslopes
```

## Table -- Pooled Models, Mixed-Effects Logistic Regression

```{r pooled-logit-fit-base}

load("model_data.RData")

pooled_logit_base <- fit_pooled_base(
  model_dfs    = model_dfs,
  model_labels = model_labels,
  family       = "binomial"
)

saveRDS(pooled_logit_base, "Plots/combined_inference/pooled_logit_base.rds")
rm(model_dfs); gc()
```

```{r table-pooled-logit-base-only}

pooled_logit_base <- readRDS("Plots/combined_inference/pooled_logit_base.rds")
pooled_logit_dir <- "Plots/combined_inference"

pooled_results_logit_base_only <- combine_pooled_results_base_only(pooled_logit_base)

pooled_logit_base_only_standalone_tex <- combined_pooled_table_base_to_standalone_tex(
  pooled_results_logit_base_only$combined_paper_table,
  model_level_labels = pooled_results_logit_base_only$model_level_labels,
  reference_label = pooled_results_logit_base_only$reference_label
)
writeLines(pooled_logit_base_only_standalone_tex, file.path(pooled_logit_dir, "combined_logit_base_only_standalone.tex"))
```

```{r pooled-logit-fit-interaction}

pooled_logit_base <- readRDS("Plots/combined_inference/pooled_logit_base.rds")

pooled_logit_interaction <- fit_pooled_interaction(pooled_logit_base, n_cores = 2)

saveRDS(pooled_logit_interaction, "Plots/combined_inference/pooled_logit_interaction.rds")
rm(pooled_logit_base, pooled_logit_interaction); gc()
```

```{r pooled-logit-fit-designinteraction}

pooled_logit_base <- readRDS("Plots/combined_inference/pooled_logit_base.rds")

pooled_logit_designinteraction <- fit_pooled_design_interaction(pooled_logit_base, n_cores = 2)

saveRDS(pooled_logit_designinteraction, "Plots/combined_inference/pooled_logit_designinteraction.rds")
rm(pooled_logit_base, pooled_logit_designinteraction); gc()
```

```{r pooled-logit-combine}

pooled_logit_base <- readRDS("Plots/combined_inference/pooled_logit_base.rds")
pooled_logit_interaction <- readRDS("Plots/combined_inference/pooled_logit_interaction.rds")
pooled_logit_designinteraction <- readRDS("Plots/combined_inference/pooled_logit_designinteraction.rds")

pooled_results_logit <- combine_pooled_results(
  base               = pooled_logit_base,
  interaction        = pooled_logit_interaction,
  design_interaction = pooled_logit_designinteraction
)

saveRDS(pooled_results_logit, "Plots/combined_inference/pooled_results_logit.rds")
rm(pooled_logit_base, pooled_logit_interaction, pooled_logit_designinteraction); gc()
```

```{r table-pooled-logit}

pooled_results_logit <- readRDS("Plots/combined_inference/pooled_results_logit.rds")
pooled_logit_dir <- "Plots/combined_inference"

write_csv(pooled_results_logit$combined_paper_table, file.path(pooled_logit_dir, "combined_logit_paper_table.csv"))

pooled_logit_latex <- combined_pooled_table_logit_to_latex(pooled_results_logit$combined_paper_table, pooled_results_logit$model_level_labels)
writeLines(pooled_logit_latex, file.path(pooled_logit_dir, "combined_logit_latex_rows.txt"))

pooled_logit_standalone_tex <- combined_pooled_table_logit_to_standalone_tex(
  pooled_results_logit$combined_paper_table,
  model_level_labels = pooled_results_logit$model_level_labels,
  reference_label = pooled_results_logit$reference_label
)
writeLines(pooled_logit_standalone_tex, file.path(pooled_logit_dir, "combined_logit_standalone.tex"))

pooled_results_logit$combined_paper_table
```
